|

### 2020-01-18 nontex/install/windows/fn_installations.Rmd
install split-diff
revealjs markdown test

# Kernel
install.packages(c('repr', 'IRdisplay', 'evaluate', 'crayon', 'pbdZMQ', 'devtools', 'uuid', 'digest'))
IRkernel::installspec()
```

@@

```
{
  "r.rterm.windows": "C:/Program Files/R/R-3.6.2/bin/x64/R.exe",
  "window.zoomLevel": 0,
  "latex-workshop.view.pdf.viewer": "external",
  "latex-workshop.view.pdf.external.synctex.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe",
  "latex-workshop.view.pdf.external.synctex.args": [
		"-forward-search",
		"%TEX%",
		"%LINE%",
		"-reuse-instance",
		"-inverse-search",
		"code \"C:\\Users\\fan\\AppData\\Local\\Programs\\Microsoft VS Code\\resources\\app\\out\\cli.js\" -r -g \"%f:%l\"",
		"%PDF%",
	],
	"latex-workshop.view.pdf.external.viewer.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe"
}
```

@@

# Selection and Overview
apm install sublime-style-column-selection
apm install minimap
apm install highlight-selected

>>>>

# Present
install.packages("revealjs")
# Kernel
install.packages(c('repr', 'IRdisplay', 'evaluate', 'crayon', 'pbdZMQ', 'devtools', 'uuid', 'digest'))
IRkernel::installspec()
```

@@

```
{
  "r.rterm.windows": "C:/Program Files/R/R-3.6.2/bin/x64/R.exe",
  "window.zoomLevel": 0,
  "latex-workshop.view.pdf.viewer": "external",
  "latex-workshop.view.pdf.external.synctex.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe",
  "latex-workshop.view.pdf.external.synctex.args": [
		"-forward-search",
		"%TEX%",
		"%LINE%",
		"-reuse-instance",
		"-inverse-search",
		"code \"C:\\Users\\fan\\AppData\\Local\\Programs\\Microsoft VS Code\\resources\\app\\out\\cli.js\" -r -g \"%f:%l\"",
		"%PDF%",
	],
	"latex-workshop.view.pdf.external.viewer.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe",
  "editor.minimap.enabled": false,
  "latex-workshop.latex.clean.fileTypes": [
    "*.aux",
    "*.bbl",
    "*.blg",
    "*.idx",
    "*.ind",
    "*.lof",
    "*.lot",
    "*.out",
    "*.toc",
    "*.acn",
    "*.acr",
    "*.alg",
    "*.glg",
    "*.glo",
    "*.gls",
    "*.fls",
    "*.log",
    "*.fdb_latexmk",
    "*.snm",
    "*.synctex(busy)",
    "*.synctex.gz(busy)",
    "*.nav",
    "*.xml",
    "*.gz",
    "*.bcf"
  ]  
}
```

@@

# Selection and Overview
apm install sublime-style-column-selection
apm install minimap
apm install highlight-selected
apm install split-diff
